Short-time expansion of Heisenberg operators in open collective quantum spin systems

### 2020-01-21 soc_squeezing/collective_paper/review/response.tex

  \red{The main lesson from Figure 1 is that the TST expansion yields
    essentially exact results right up until a sudden and drastic
    departure that can be diagnosed by inspection.  {\bf The breakdown
      of the TST expansion in Figure 1 is marked by an unphysical
      squeezing parameter $\xi^2<0$, which occurs due to individual
      correlators taking unphysical values with
      $\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$.  Going up
      through order $M=70$ in the TST expansion does not significantly
      increase the breakdown time $t_{\t{break}}^{(M)}$, and in some
      cases even shortens $t_{\t{break}}^{(M)}$.}  The sudden and
    drastic departure from virtually exact results is consistent with
    the limitations of the TST expansion discussed at the end of
    Section II.  Specifically, we identify three possible mechanisms
    for breakdown:
    \begin{enumerate*}
    \item a rapid growth in the order $M$ necessary for the TST
      expansion to converge,
    \item the growth of numerical errors in excessively large terms of
      the TST expansion, and
    \item the formal breakdown of the perturbative expansion in the
      time $t$.
    \end{enumerate*}
    In all of these cases, a detailed cancellation eventually ceases
    to occur between large terms at high orders in the TST expansion.
    These large terms grow with the time $t$ raised to some large
    power (as high as $M$), and therefore rapidly yield wildly
    unphysical results.  In contrast to other approximate methods such
    as the cumulant expansion[58], the TST expansion can thus diagnose
    its own breakdown, which is an important feature when working in
    parameter regimes that are inaccessible via other means to compute
    correlators.}

  by (top of page 5 in the new text):

  \green{The main lesson from Figure 1 is that the TST expansion
    yields essentially exact results right up until a sudden and
    drastic departure that can be diagnosed by inspection.  {\bf The
      breakdown of the TST expansion in Figure 1 induces an unphysical
      squeezing parameter $\xi^2<0$.  In general, however, there is no
      fundamental relationship between the breakdown of the TST
      expansion and the conditions for a physical squeezing parameter
      $\xi^2$.  A proper diagnosis of breakdown therefore requires
      inspection of the correlators $\bk{\hat\S_{\v n}\p{t}}$ used to
      compute the squeezing parameter $\xi^2$, which upon breakdown
      will rapidly take unphysical values with
      $\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$ (see
      Appendix L for an example).}  The sudden and drastic departure
    from virtually exact results is consistent with the limitations of
    the TST expansion discussed at the end of Section II.
    Specifically, we identify three possible mechanisms for breakdown:
    \begin{enumerate*}
    \item a rapid growth in the order $M$ necessary for the TST
      expansion to converge,
    \item the growth of numerical errors in excessively large terms of
      the TST expansion, and
    \item the formal breakdown of the perturbative expansion in the
      time $t$.
    \end{enumerate*}
    In all of these cases, a detailed cancellation eventually ceases
    to occur between large terms at high orders in the TST expansion.
    These large terms grow with the time $t$ raised to some large
    power (as high as $M$), and therefore rapidly yield wildly
    unphysical results.  In contrast to other approximate methods such
    as the cumulant expansion[58], the TST expansion can thus diagnose
    its own breakdown, which is an important feature when working in
    parameter regimes that are inaccessible via other means to compute
    correlators.  {\bf Note that, due to the breakdown mechanisms of
      the TST expansion, going up through order $M=70$ does not
      significantly increase the breakdown time $t_{\t{break}}^{(M)}$
      in Figure 1, and in some cases even shortens
      $t_{\t{break}}^{(M)}$.}}

  Note that we used bold text to help identify the changes above; the
  manuscript itself does not make these changes bold.  We have also
  added a short new appendix (L) to provide an example of breakdown
  without an unphysical squeezing parameter.  We hope that these
  changes clarify subtleties related to the referee's question.

@@

  \red{Note that the OAT model is a special case of the zero-field
    Ising model, whose quantum dynamics admits an exact analytic
    solution even in the presence of decoherence[62].  We will
    benchmark our calculations using these analytical OAT results
    wherever applicable (see Appendix J, as well as the Supplementary
    Material of Ref.~[14]).}

  to:

  \green{Note that the OAT model is a special case of the zero-field
    Ising model, whose quantum dynamics admits an exact analytic
    solution even in the presence of decoherence[64].  The approximate
    and numerics-oriented TST expansion is therefore an inappropriate
    tool for studying the OAT model, which will merely serve as an
    exactly solvable benchmark of our methods.  Wherever applicable,
    we will provide exact results for the OAT model (see Appendix K,
    as well as the Supplementary Material of Ref.~[14]).}

\item Concerning the final question, about squeezing with strong
  decoherence:

@@

  \blue{3. I am surprised by the results from the strong decoherence
    regimes in Fig.~2, which shows that twist and-turn (TNT) model is
    much more robust than OAT and TAT. Is this physical or just an
    artifact from numerical errors. To rule out the latter, I suggest
    the authors check the results in the strong decoherence regime by
    studying a smaller system, where Monte Carlo simulation is
    accessible and can be used as a comparison. If this result is
    indeed physical, if would be very helpful if the authors could
    comment on the reason?}

  We thank the referee for their careful attention to our results.  We
  agree that our findings warrant a comment on why TNT performs better
  than OAT or TAT in the presence of decoherence.  We have therefore
  rewritten some of the last paragraph of section III (end of page 5,
  beginning of page 6), replacing:

  \red{The results in Figure 2 show that TNT is much more robust to
    single-spin decoherence than OAT or TAT, a finding that could not
    necessarily be deduced from the weak-decoherence simulations
    presented in Figure 1.  Strong-decoherence computations of this
    sort were used to put lower bounds...}

  by:

  \green{The results in Figure 2 show that the TNT model can generate
    more squeezing than the OAT or TAT models in the presence of
    strong decoherence.  The better performance of TNT is in part a
    consequence of the fact that TNT initially generates squeezing at
    a faster rate than OAT or TAT, thereby allowing it to produce more
    squeezing before the degrading effects of decoherence kick in.  We
    corroborate this finding with quantum trajectory simulations of a
    small system in Appendix M.  Strong-decoherence computations of
    the sort used for Figure 2 put lower bounds...}

  The new appendix includes Monte Carlo simulations of a small system
  with sufficiently strong decoherence to reproduce the improved
  performance of TNT.  We hope that these additions address the
  referee's questions about figure 2 to a satisfactory degree.

### 2020-01-21 soc_squeezing/collective_paper/collective_spin.tex
committing final changes to collective spin paper and codes

The Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT} squeeze the
initial product state $\ket{\X}\propto\p{\ket\up+\ket\dn}^{\otimes N}$
with $\hat S_\x\ket{\X}=S\ket{\X}$.  Our measure of spin squeezing is
the directionally-unbiased Ramsey squeezing parameter determined by
the maximal gain in resolution $\Delta\phi$ of a phase angle $\phi$
over that achieved by any spin-polarized product state
(e.g.~$\ket{\X}$)\cite{wineland1992spin, ma2011quantum},
\begin{align}
  \xi^2
  \equiv \f{\p{\Delta\phi_{\t{min}}}^2}{\p{\Delta\phi_{\t{polarized}}}^2}
  = \f{N}{\abs{\braket{\uv S}}^2}
  \min_{\substack{\v v\perp\bk{\uv S}\\\v v\cdot\v v=1}}
  \Bk{\p{\uv S\cdot\v v}^2},
  \label{eq:squeezing}
\end{align}
where $\uv S\equiv\p{\hat S_\x,\hat S_\y,\hat S_\z}$ is a collective
spin operator-valued vector, the minimization is performed over all
unit vectors $\v v$ orthogonal to the mean spin vector $\bk{\uv S}$,
and for brevity we have suppressed the explicit time dependence of
operators in Eq.~\eqref{eq:squeezing}.  This squeezing parameter is
entirely determined by one- and two-spin correlators of the form
$\bk{\hat S_\a}$ and $\bk{\hat S_\a \hat S_\b}$.  For the unitary
dynamics discussed in this work, these correlators are obtainable via
exact simulations of quantum dynamics in the $\p{N+1}$-dimensional
Dicke manifold of states $\set{\ket{S,m}}$ with net spin $S$ and spin
projection $m$ onto the $z$ axis, i.e.~with
$\bk{S,m|\uv S^2|S,m}=S\p{S+1}$ and $\bk{S,m|\hat S_\z|S,m}=m$ for
$m\in\set{-S,-S+1,\cdots,S}$.  In the presence of single-spin or
collective decoherence, meanwhile, these correlators are obtainable
with the collective-spin quantum trajectory Monte Carlo method
developed in ref.~\cite{zhang2018montecarlo}.  In this work, these
exact and quantum trajectory simulations will be used to benchmark the
TST expansion in Eq.~\eqref{eq:TST}.

\begin{figure}
  \centering
  \subfloat[Squeezing with unitary dynamics
  \label{fig:squeezing_unitary}]
  {\includegraphics{unitary.pdf}} \\
  \subfloat[Squeezing with decoherence:
  $\gamma_-=\gamma_+=\gamma_\z=\chi$
  \label{fig:squeezing_incoherent}]
  {\includegraphics{decoherence_weak.pdf}}
  \caption{Spin squeezing of $N=10^4$ spins initially in $\ket\X$
    under \sref{fig:squeezing_unitary} unitary and
    \sref{fig:squeezing_incoherent} non-unitary dynamics, computed
    using exact methods (solid lines), quantum trajectory simulations
    (dots), and the TST expansion in Eq.~\eqref{eq:TST} with $M=35$
    (dashed lines).  Solid circles mark the times at which the TST
    expansion gives an unphysical result with $\xi^2<0$.}
  \label{fig:benchmarking}
\end{figure}

Figure \ref{fig:benchmarking} compares the squeezing parameter $\xi^2$
for $N=10^4$ spins initially in the state $\ket{\X}$ evolved under the
Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}, as computed via
both benchmarking simulations and the TST expansion in
Eq.~\eqref{eq:TST} with $M=35$.  Squeezing is shown for both unitary
dynamics (Figure \ref{fig:squeezing_unitary}), as well as non-unitary
dynamics in the presence of spontaneous decay, excitation, and
dephasing of individual spins at rates $\chi$ (Figure
\ref{fig:squeezing_incoherent}), respectively described by the sets of
jump operators $\J_\a\equiv\set{\hat s_\a^{(j)}}$ with corresponding
decoherence rates $\gamma_\a=\chi$ for $\a\in\set{-,+,\z}$.  The
results shown in Figure \ref{fig:benchmarking} were computed in a
rotated basis with
$\p{\hat s_\z,\hat s_\x}\to\p{\hat s_\x,-\hat s_\z}$ and
$\ket\X\to\ket{-\Z}\equiv\ket\dn^{\otimes N}$, as well as appropriate
transformations of the Hamiltonian and jump operators.  The only
effects of this rotation on the results presented in Figure
\ref{fig:benchmarking} are to
\begin{enumerate*}
\item reduce the time it takes to compute correlators
  $\bk{\hat\O\p{t}}$ with the TST expansion, and
\item prolong the time for which the TST expansion of TNT results
  agree with benchmarking simulations.
\end{enumerate*}
The speedup in a different basis occurs because for the initial state
$\ket{-\Z}$, all initial-time correlators $\bk{\hat S_{\v m}}$ are
zero unless $m_+=m_-=0$, and all non-zero correlators take $O\p{1}$
(i.e.~constant in $N$) time to compute, rather than $O\p{N}$ time (see
Appendix \ref{sec:initial_conditions}).  In total, the use of a
rotated basis reduces the computation time of initial-time correlators
from $O\p{M^3N}$ to $O\p{M}$.  The reason for prolonged agreement of
TNT results in a rotated basis is not entirely understood, and
provides a clue into the precise mechanism by which the TST expansion
breaks down (discussed below).  We defer a detailed study of this
breakdown to future work.

The main lesson from Figure \ref{fig:benchmarking} is that the TST
expansion yields essentially exact results right up until a sudden and
drastic departure that can be diagnosed by inspection.  The breakdown
of the TST expansion in Figure \ref{fig:benchmarking} induces an
unphysical squeezing parameter $\xi^2<0$.  In general, however, there
is no fundamental relationship between the breakdown of the TST
expansion and the conditions for a physical squeezing parameter
$\xi^2$.  A proper diagnosis of breakdown therefore requires
inspection of the correlators $\bk{\hat\S_{\v n}\p{t}}$ used to
compute the squeezing parameter $\xi^2$, which upon breakdown will
rapidly take unphysical values with
$\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$.  The sudden and
drastic departure from virtually exact results is consistent with the
limitations of the TST expansion discussed at the end of Section
\ref{sec:theory}.  Specifically, we identify three possible mechanisms
for breakdown:
\begin{enumerate*}
\item a rapid growth in the order $M$ necessary for the TST expansion
  to converge,
\item the growth of numerical errors in excessively large terms of the
  TST expansion, and
\item the formal breakdown of the perturbative expansion in the time
  $t$.
\end{enumerate*}
In all of these cases, a detailed cancellation eventually ceases to
occur between large terms at high orders in the TST expansion.  These
large terms grow with the time $t$ raised to some large power (as high
as $M$), and therefore rapidly yield wildly unphysical results.  In
contrast to other approximate methods such as the cumulant
expansion\cite{meiser2010steadystate}, the TST expansion can thus
diagnose its own breakdown, which is an important feature when working
in parameter regimes that are inaccessible via other means to compute
correlators.  Note that, due to the breakdown mechanisms of the TST
expansion, going up through order $M=70$ does not significantly
increase the breakdown time $t_{\t{break}}^{(M)}$ in Figure
\ref{fig:benchmarking}, and in some cases even shortens
$t_{\t{break}}^{(M)}$.

Although the TST expansion breaks down at short times, it has two key
advantages over the quantum trajectory Monte Carlo method to compute
correlators in the presence of decoherence.  First, computing spin
correlators with the TST expansion is generally faster and requires
fewer computing resources.  The TST expansion results in Figure
\ref{fig:squeezing_incoherent}, for example, take $\sim10$ seconds to
compute with a single CPU on modern computing hardware.  The quantum
trajectory Monte Carlo results in the same figure, meanwhile, take
$\sim10^4$ CPU hours to compute on similar hardware; the bulk of this
time is spent performing sparse matrix-vector multiplication, leaving
little room to further optimize serial runtime.  Parallelization can
reduce actual runtime of the Monte Carlo simulations to $\sim10$ hours
by running all trajectories at once, but at the cost of greatly
increasing computing resource requirements.  Though it may be possible
to further speed up quantum trajectory Monte Carlo simulations by
introducing new truncation schemes, any modifications
\begin{enumerate*}
\item should be made carefully to ensure that simulations still yield
  correct results, and
\item are unlikely to bridge the orders of magnitude in computing
  resource requirements.
\end{enumerate*}

@@

The second advantage of the TST expansion is the capability to compute
spin correlators in strong-decoherence regimes of large systems that
are entirely inaccessible to other methods.  As an example, Figure
\ref{fig:decoherence_strong} shows squeezing of $N=10^4$ spins
initially in $\ket{\X}$, undergoing spontaneous decay, excitation, and
dephasing of individual spins at rates
$\gamma_-=\gamma_+=\gamma_\z=100\chi$.  The system size in these
simulations is too large for straightforward application of exact
methods for open quantum systems.  Quantum trajectory Monte Carlo
simulations, meanwhile, take a prohibitively long time to converge
with such strong decoherence due to the multiplicity of quantum
trajectories that require averaging.

The results in Figure \ref{fig:decoherence_strong} show that the TNT
model can generate more squeezing than the OAT or TAT models in the
presence of strong decoherence.  The better performance of TNT is a
consequence of the fact that TNT initially generates squeezing at a
faster rate than OAT or TAT, thereby allowing it to produce more
squeezing before the degrading effects of decoherence kick in.  We
corroborate this finding with quantum trajectory simulations of a
small system in Appendix \ref{sec:small_system}.  Strong-decoherence
computations of the sort used for Figure \ref{fig:decoherence_strong}
were used to put lower bounds on theoretically achievable spin
squeezing via TAT with decoherence in
Ref.~[\citenum{he2019engineering}], exemplifying a concrete and
practical application of the TST expansion and the collective-spin
structure constants calculated in this work.

@@

\begin{figure*}
  \centering
  \begin{minipage}{0.49\linewidth}
    \subfloat[Two-time correlator
    $C\p{t}\equiv\abs{C\p{t}}\exp\sp{i\phi\p{t}}$.
    \label{fig:two_time}]
    {\includegraphics{two_time.pdf}}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
    \subfloat[Squared commutator $D\p{t}$.
    \label{fig:four_point}]
    {\includegraphics{FPC.pdf}}
  \end{minipage}
  \caption{The two-time connected correlator $C\p{t}$ and squared
    commutator $D\p{t}$, respectively defined in
    Eqs.~\eqref{eq:two_time} and \eqref{eq:four_point}, for $N=10^4$
    spins initially in the polarized state
    $\ket{\X}\propto\p{\ket\up+\ket\dn}^{\otimes N}$ evolving under
    the squeezing Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}.
    Results are shown for both unitary dynamics (solid lines) and
    non-unitary dynamics with $\gamma_-=\gamma_+=\gamma_\z=100\chi$
    (dashed lines), computed using the TST expansion in
    Eq.~\eqref{eq:TST} with $M=20$.}
  \label{fig:multi_time}
\end{figure*}

@@

\vfill
\onecolumngrid
\appendix

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robustness of squeezing generated by the twist-and-turn (TNT)
  model}
\label{sec:small_system}

% \begin{figure}
%   \centering
%   \includegraphics{decoherence_strong_small.pdf}
%   \caption{Spin squeezing of $N=100$ spins initially in $\ket\X$ with
%     spontaneous decay, excitation, and dephasing of individual spins
%     at rates $\gamma_-=\gamma_+=\gamma_\z=2\chi$.  Computed computed
%     using exact methods (solid line), quantum trajectory simulations
%     with $10^4$ trajectories (dots), and the TST expansion in
%     Eq.~\eqref{eq:TST} with $M=35$ (dashed lines).}
%   \label{fig:decoherence_strong_small}
% \end{figure}

>>>>

The Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT} squeeze the
initial product state $\ket\X\propto\p{\ket\up+\ket\dn}^{\otimes N}$
with $\hat S_\x\ket\X=S\ket\X$.  Our measure of spin squeezing is the
directionally-unbiased Ramsey squeezing parameter determined by the
maximal gain in resolution $\Delta\phi$ of a phase angle $\phi$ over
that achieved by any spin-polarized product state
(e.g.~$\ket\X$)\cite{wineland1992spin, ma2011quantum},
\begin{align}
  \xi^2
  \equiv \f{\p{\Delta\phi_{\t{min}}}^2}{\p{\Delta\phi_{\t{polarized}}}^2}
  = \f{N}{\abs{\braket{\uv S}}^2}
  \min_{\substack{\v v\perp\bk{\uv S}\\\v v\cdot\v v=1}}
  \Bk{\p{\uv S\cdot\v v}^2},
  \label{eq:squeezing}
\end{align}
where $\uv S\equiv\p{\hat S_\x,\hat S_\y,\hat S_\z}$ is a collective
spin operator-valued vector, the minimization is performed over all
unit vectors $\v v$ orthogonal to the mean spin vector $\bk{\uv S}$,
and for brevity we have suppressed the explicit time dependence of
operators in Eq.~\eqref{eq:squeezing}.  This squeezing parameter is
entirely determined by one- and two-spin correlators of the form
$\bk{\hat S_\a}$ and $\bk{\hat S_\a \hat S_\b}$.  For the unitary
dynamics discussed in this work, these correlators are obtainable via
exact simulations of quantum dynamics in the $\p{N+1}$-dimensional
Dicke manifold of states $\set{\ket{S,m}}$ with net spin $S$ and spin
projection $m$ onto the $z$ axis, i.e.~with
$\bk{S,m|\uv S^2|S,m}=S\p{S+1}$ and $\bk{S,m|\hat S_\z|S,m}=m$ for
$m\in\set{-S,-S+1,\cdots,S}$.  In the presence of single-spin or
collective decoherence, meanwhile, these correlators are obtainable
with the collective-spin quantum trajectory Monte Carlo method
developed in ref.~\cite{zhang2018montecarlo}.  In this work, these
exact and quantum trajectory simulations will be used to benchmark the
TST expansion in Eq.~\eqref{eq:TST}.

\begin{figure}
  \centering
  \subfloat[Squeezing with unitary dynamics
  \label{fig:squeezing_unitary}]
  {\includegraphics{unitary.pdf}} \\
  \subfloat[Squeezing with decoherence:
  $\gamma_-=\gamma_+=\gamma_\z=\chi$
  \label{fig:squeezing_dec}]
  {\includegraphics{decoherence_weak.pdf}}
  \caption{Spin squeezing of $N=10^4$ spins initially in $\ket\X$
    under \sref{fig:squeezing_unitary} unitary and
    \sref{fig:squeezing_dec} non-unitary dynamics, computed using
    exact methods (solid lines), quantum trajectory simulations
    (dots), and the TST expansion in Eq.~\eqref{eq:TST} with $M=35$
    (dashed lines).  Solid circles mark the times at which the TST
    expansion gives an unphysical result with $\xi^2<0$.}
  \label{fig:benchmarking}
\end{figure}

Figure \ref{fig:benchmarking} compares the squeezing parameter $\xi^2$
for $N=10^4$ spins initially in the state $\ket\X$ evolved under the
Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}, as computed via
both benchmarking simulations and the TST expansion in
Eq.~\eqref{eq:TST} with $M=35$.  Squeezing is shown for both unitary
dynamics (Figure \ref{fig:squeezing_unitary}), as well as non-unitary
dynamics in the presence of spontaneous decay, excitation, and
dephasing of individual spins at rates $\chi$ (Figure
\ref{fig:squeezing_dec}), respectively described by the sets of jump
operators $\J_\a\equiv\set{\hat s_\a^{(j)}}$ with corresponding
decoherence rates $\gamma_\a=\chi$ for $\a\in\set{-,+,\z}$.  The
results shown in Figure \ref{fig:benchmarking} were computed in a
rotated basis with
$\p{\hat s_\z,\hat s_\x}\to\p{\hat s_\x,-\hat s_\z}$ and
$\ket\X\to\ket{-\Z}\equiv\ket\dn^{\otimes N}$, as well as appropriate
transformations of the Hamiltonian and jump operators.  The only
effects of this rotation on the results presented in Figure
\ref{fig:benchmarking} are to
\begin{enumerate*}
\item reduce the time it takes to compute correlators
  $\bk{\hat\O\p{t}}$ with the TST expansion, and
\item prolong the time for which the TST expansion of TNT results
  agree with benchmarking simulations.
\end{enumerate*}
The speedup in a different basis occurs because for the initial state
$\ket{-\Z}$, all initial-time correlators $\bk{\hat S_{\v m}}$ are
zero unless $m_+=m_-=0$, and all non-zero correlators take $O\p{1}$
(i.e.~constant in $N$) time to compute, rather than $O\p{N}$ time (see
Appendix \ref{sec:initial_conditions}).  In total, the use of a
rotated basis reduces the computation time of initial-time correlators
from $O\p{M^3N}$ to $O\p{M}$.  The reason for prolonged agreement of
TNT results in a rotated basis is not entirely understood, and
provides a clue into the precise mechanism by which the TST expansion
breaks down (discussed below).  We defer a detailed study of this
breakdown to future work.

The main lesson from Figure \ref{fig:benchmarking} is that the TST
expansion yields essentially exact results right up until a sudden and
drastic departure that can be diagnosed by inspection.  The breakdown
of the TST expansion in Figure \ref{fig:benchmarking} induces an
unphysical squeezing parameter $\xi^2<0$.  In general, however, there
is no fundamental relationship between the breakdown of the TST
expansion and the conditions for a physical squeezing parameter
$\xi^2$.  A proper diagnosis of breakdown therefore requires
inspection of the correlators $\bk{\hat\S_{\v n}\p{t}}$ used to
compute the squeezing parameter $\xi^2$, which upon breakdown will
rapidly take unphysical values with
$\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$ (see Appendix
\ref{sec:breakdown} for an example).  The sudden and drastic departure
from virtually exact results is consistent with the limitations of the
TST expansion discussed at the end of Section \ref{sec:theory}.
Specifically, we identify three possible mechanisms for breakdown:
\begin{enumerate*}
\item a rapid growth in the order $M$ necessary for the TST expansion
  to converge,
\item the growth of numerical errors in excessively large terms of the
  TST expansion, and
\item the formal breakdown of the perturbative expansion in the time
  $t$.
\end{enumerate*}
In all of these cases, a detailed cancellation eventually ceases to
occur between large terms at high orders in the TST expansion.  These
large terms grow with the time $t$ raised to some large power (as high
as $M$), and therefore rapidly yield wildly unphysical results.  In
contrast to other approximate methods such as the cumulant
expansion\cite{meiser2010steadystate}, the TST expansion can thus
diagnose its own breakdown, which is an important feature when working
in parameter regimes that are inaccessible via other means to compute
correlators.  Note that, due to the breakdown mechanisms of the TST
expansion, going up through order $M=70$ does not significantly
increase the breakdown time $t_{\t{break}}^{(M)}$ in Figure
\ref{fig:benchmarking}, and in some cases even shortens
$t_{\t{break}}^{(M)}$.

Although the TST expansion breaks down at short times, it has two key
advantages over the quantum trajectory Monte Carlo method to compute
correlators in the presence of decoherence.  First, computing spin
correlators with the TST expansion is generally faster and requires
fewer computing resources.  The TST expansion results in Figure
\ref{fig:squeezing_dec}, for example, take $\sim10$ seconds to compute
with a single CPU on modern computing hardware.  The quantum
trajectory Monte Carlo results in the same figure, meanwhile, take
$\sim10^4$ CPU hours to compute on similar hardware; the bulk of this
time is spent performing sparse matrix-vector multiplication, leaving
little room to further optimize serial runtime.  Parallelization can
reduce actual runtime of the Monte Carlo simulations to $\sim10$ hours
by running all trajectories at once, but at the cost of greatly
increasing computing resource requirements.  Though it may be possible
to further speed up quantum trajectory Monte Carlo simulations by
introducing new truncation schemes, any modifications
\begin{enumerate*}
\item should be made carefully to ensure that simulations still yield
  correct results, and
\item are unlikely to bridge the orders of magnitude in computing
  resource requirements.
\end{enumerate*}

@@

The second advantage of the TST expansion is the capability to compute
spin correlators in strong-decoherence regimes of large systems that
are entirely inaccessible to other methods.  As an example, Figure
\ref{fig:decoherence_strong} shows squeezing of $N=10^4$ spins
initially in $\ket\X$, undergoing spontaneous decay, excitation, and
dephasing of individual spins at rates
$\gamma_-=\gamma_+=\gamma_\z=100\chi$.  The system size in these
simulations is too large for straightforward application of exact
methods for open quantum systems.  Quantum trajectory Monte Carlo
simulations, meanwhile, take a prohibitively long time to converge
with such strong decoherence due to the multiplicity of quantum
trajectories that require averaging.

The results in Figure \ref{fig:decoherence_strong} show that the TNT
model can generate more squeezing than the OAT or TAT models in the
presence of strong decoherence.  The better performance of TNT is in
part a consequence of the fact that TNT initially generates squeezing
at a faster rate than OAT or TAT, thereby allowing it to produce more
squeezing before the degrading effects of decoherence kick in.  We
corroborate this finding with quantum trajectory simulations of a
smaller system in Appendix \ref{sec:strong_dec}.  Strong-decoherence
computations of the sort used for Figure \ref{fig:decoherence_strong}
put lower bounds on theoretically achievable spin squeezing via TAT
with decoherence in Ref.~[\citenum{he2019engineering}], exemplifying a
concrete and practical application of the TST expansion and the
collective-spin structure constants calculated in this work.

@@

\begin{figure*}
  \centering
  \begin{minipage}{0.49\linewidth}
    \subfloat[Two-time correlator
    $C\p{t}\equiv\abs{C\p{t}}\exp\sp{i\phi\p{t}}$.
    \label{fig:two_time}]
    {\includegraphics{two_time.pdf}}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
    \subfloat[Squared commutator $D\p{t}$.
    \label{fig:four_point}]
    {\includegraphics{FPC.pdf}}
  \end{minipage}
  \caption{The two-time connected correlator $C\p{t}$ and squared
    commutator $D\p{t}$, respectively defined in
    Eqs.~\eqref{eq:two_time} and \eqref{eq:four_point}, for $N=10^4$
    spins initially in the polarized state
    $\ket\X\propto\p{\ket\up+\ket\dn}^{\otimes N}$ evolving under the
    squeezing Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}.
    Results are shown for both unitary dynamics (solid lines) and
    non-unitary dynamics with
    $\gamma_-=\gamma_+=\gamma_\z=\gamma_0=100\chi$ (dashed lines),
    computed using the TST expansion in Eq.~\eqref{eq:TST} with
    $M=20$.}
  \label{fig:multi_time}
\end{figure*}

@@

\onecolumngrid
\appendix

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Diagnosing breakdown of the TST expansion}
\label{sec:breakdown}

In Figure \ref{fig:benchmarking} of the main text, the TST expansion
provided nearly exact results for squeezing until a sudden departure
that quickly resulted in an unphysical squeezing parameter, $\xi^2<0$.
In general, however, there is no fundamental relationship between the
breakdown of the TST expansion and the conditions for a physical
squeezing parameter $\xi^2$.  A proper diagnosis of breakdown
therefore requires inspection of the correlators $\bk{\S_{\v n}\p{t}}$
used to compute the squeezing parameter $\xi^2$, which upon breakdown
will rapidly take unphysical values with
$\abs{\bk{\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$.  As an example,
Figure \ref{fig:unitary_small} shows the squeezing parameter $\xi^2$
throughout decoherence-free evolution of $N=100$ spins initially in
the state $\ket\X$.  In this example, the squeezing computed by the
TST expansion for the TAT model diverges from the exact answer without
an immediate and obvious signature of breakdown.  Nonetheless,
breakdown can still be diagnosed by inspection of individual
correlators, as shown in Figure \ref{fig:correlator_example}, where we
plot $\t{Im}\bk{S_+^2}$ as a function of time for $N=100$ spins
evolving under the TAT without decoherence.  Figure
\ref{fig:correlator_example} shows that breakdown clearly occurs
around $N\chi t\lesssim7$, when the correlator $\bk{S_+^2}$ begins to
diverge to values $\gtrsim S^2=\p{N/2}^2=2500$ in magnitude.  A joint
inspection of figures \ref{fig:unitary_small} and
\ref{fig:correlator_example} suffice to trace the anomalous behavior
of $\xi^2$ from $N\chi t\approx 7$ back to $N\chi t\approx 6$, when it
first took a sudden turn before becoming unphysical at
$N\chi t\approx 8$.

\begin{figure}
  \centering
  \includegraphics{unitary_small.pdf}
  \caption{Spin squeezing throughout decoherence-free evolution of
    $N=100$ spins initially in the state $\ket\X$, computed using both
    exact methods (solid lines) and the TST expansion in
    Eq.~\eqref{eq:TST} with $M=35$ (dashed lines).  Solid circles mark
    the times at which the TST expansion gives an unphysical result
    with $\xi^2<0$.}
  \label{fig:unitary_small}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{correlator_example.pdf}
  \caption{A collective spin correlator in the TAT model with $N=100$
    spins and no decoherence, computed using the TST expansion with
    $M=35$.  The divergence of correlators of this sort can be used to
    diagnose the breakdown of the TST expansion.}
  \label{fig:correlator_example}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spin squeezing with strong decoherence}
\label{sec:strong_dec}

Here we provide supplementary evidence of our finding in Section
\ref{sec:squeezing} that the TNT model can produce more squeezing than
the OAT or TAT models in the presence of strong decoherence.  To this
end, Figure \ref{fig:sqz_dec_scaling} shows the minimal squeezing
parameter $\xi^2_{\t{min}}$ achievable with $N=100$ spins through the
OAT, TAT, and TNT models as a function of the rate $\gamma_0$ at which
individual spins undergo spontaneous decay, excitation, and dephasing.
These results were computed with quantum trajectory simulations, with
$10^3$ trajectories per data point.  While the OAT and TAT models
produce more squeezing than TNT model with weak decoherence, this
squeezing falls off faster with an increasing decoherence rate
$\gamma_0$.  The relative robustness of TNT is in part a consequence
of the fact that TNT initially generates squeezing at a faster rate
than OAT or TAT, thereby allowing it to produce more squeezing before
the degrading effects of decoherence kick in.

\begin{figure}
  \centering
  \includegraphics{sqz_dec_scaling.pdf}
  \caption{Optimal spin squeezing of $N=100$ spins undergoing
    spontaneous decay, excitation, and dephasing at rates
    $\gamma_-=\gamma_+=\gamma_\z=\gamma_0$, computed using quantum
    trajectory simulations with $10^3$ trajectories per data point.}
  \label{fig:sqz_dec_scaling}
\end{figure}
